Improving the prospects for multimessenger astronomy with \earlywarning\ detection of compact binary coalescence.

### 2011-05-16 method.tex
Rearranged some section headings
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@752 ccdd05d5-56c1-461a-bf98-85f6876523b4

In this section we describe a decomposition of the compact binary parameter
space that reduces low latency filtering cost sufficiently to allow for the
possibility of \earlywarning\ detection with modest computing requirements.  We
expand on the ideas of~\cite{Marion2004, Buskulic2010} that describe a
multiband decomposition of the compact binary parameter space that resulted in
search with $\sim$minutes latency in LIGO's S6 and Virgo's VSR2 science runs.
We combine this with the orthogonal decomposition described
in~\cite{Cannon:2010p10398} that exploits the redundancy of the template banks.

Inspiral signals are parameterized by a set of intrinsic parameters
$\bar{\theta}$ that determine the amplitude and phase evolution of the observed
binary signals.  Searches for gravitational waves from compact binary
coalescence typically employ matched filter banks, called template banks,
\cite{findchirppaper} that discretely sample the possible intrinsic parameters.
The filter models of the waveforms, known as templates are weighted by the
detector noise amplitude spectral density, $x(t,\bar{\theta})$ and filtered
against the whitened detector data.  A sufficient number of templates are
chosen to assure a minimal loss of SNR~\cite{Owen:1995tm,Owen:1998dk}.  To
construct a template bank, matched filters are chosen with discrete signal
parameters $\theta_1,\, \theta_2,\, \cdots$, $\theta_N$, such that any possible
signal will have a cross-correlation of $\geq0.97$ with at least one template.
Such a template bank is said to have a 97\% {\em minimum match}. For systems
where the effects of spin can be ignored, the intrinsic parameters are the
component masses of the binary, $\bar{\theta} = (m_1, m_2)$.

@@

@@

\subsection{Selectively reducing the sample rate of the data and template waveforms}

@@

\subsection{Reducing the number of filters with the singular value
decomposition}

>>>>

In this section we describe a decomposition of the compact binary parameter
space that reduces low latency filtering cost sufficiently to allow for the
possibility of \earlywarning\ detection with modest computing requirements.  We
expand on the ideas of~\cite{Marion2004, Buskulic2010} that describe a
multiband decomposition of the compact binary parameter space that resulted in
search with $\sim$minutes latency in \LIGO's S6 and Virgo's VSR2 science runs.
We combine this with the orthogonal decomposition described
in~\cite{Cannon:2010p10398} that exploits the redundancy of the template banks.

\subsection{Conventional \CBC{} matched filter searches}

Inspiral signals are parameterized by a set of intrinsic parameters
$\bar{\theta}$ that determine the amplitude and phase evolution of the observed
binary signals.  Searches for gravitational waves from compact binary
coalescence typically employ matched filter banks, called template banks,
\cite{findchirppaper} that discretely sample the possible intrinsic parameters.
The filter models of the waveforms, known as templates are weighted by the
detector noise amplitude spectral density, $x(t,\bar{\theta})$ and filtered
against the whitened detector data.  A sufficient number of templates are
chosen to assure a minimal loss of \SNR~\cite{Owen:1995tm,Owen:1998dk}.  To
construct a template bank, matched filters are chosen with discrete signal
parameters $\theta_1,\, \theta_2,\, \cdots$, $\theta_N$, such that any possible
signal will have a cross-correlation of $\geq0.97$ with at least one template.
Such a template bank is said to have a 97\% {\em minimum match}. For systems
where the effects of spin can be ignored, the intrinsic parameters are the
component masses of the binary, $\bar{\theta} = (m_1, m_2)$.

@@

\subsection{Proposed method}

@@

\subsubsection{Selectively reducing the sample rate of the data and template waveforms}

@@

\subsubsection{Reducing the number of filters with the singular value
decomposition}
